Quasi-universal acceptance of basic science in the US

### 2024-09-19 paper.Rmd
add anonymized link before pus submission

In a series of four pre-registered online studies (total n = 782), we asked US participants questions about well-established scientific facts. For each question, we asked participants what they thought the correct answer was (testing their knowledge of science), we informed them of the scientifically accepted answer, and asked them whether they accepted it (measuring their trust in basic science). We also measured participants’ trust in science using standard measures, as well as their beliefs in various conspiracy theories and their tendency to engage in conspiratorial thinking. The four studies, including materials, hypotheses, and analyses, were pre-registered and all materials and data are accessible via the Open Science Framework (OSF). The differences between the four studies are summarized presently, and the methods are detailed below.

>>>>

In a series of four pre-registered online studies (total n = 782), we asked US participants questions about well-established scientific facts. For each question, we asked participants what they thought the correct answer was (testing their knowledge of science), we informed them of the scientifically accepted answer, and asked them whether they accepted it (measuring their trust in basic science). We also measured participants’ trust in science using standard measures, as well as their beliefs in various conspiracy theories and their tendency to engage in conspiratorial thinking. The four studies, including materials, hypotheses, and analyses, were pre-registered and all materials and data are accessible via the Open Science Framework (https://osf.io/8utsj/?view_only=364478f01fc548d0a42b9962918d871d). The differences between the four studies are summarized presently, and the methods are detailed below.

### 2024-09-19 paper.tex
add anonymized link before pus submission

In a series of four pre-registered online studies (total n = 782), we asked US participants questions about well-established scientific facts. For each question, we asked participants what they thought the correct answer was (testing their knowledge of science), we informed them of the scientifically accepted answer, and asked them whether they accepted it (measuring their trust in basic science). We also measured participants' trust in science using standard measures, as well as their beliefs in various conspiracy theories and their tendency to engage in conspiratorial thinking. The four studies, including materials, hypotheses, and analyses, were pre-registered and all materials and data are accessible via the Open Science Framework (OSF). The differences between the four studies are summarized presently, and the methods are detailed below.

>>>>

In a series of four pre-registered online studies (total n = 782), we asked US participants questions about well-established scientific facts. For each question, we asked participants what they thought the correct answer was (testing their knowledge of science), we informed them of the scientifically accepted answer, and asked them whether they accepted it (measuring their trust in basic science). We also measured participants' trust in science using standard measures, as well as their beliefs in various conspiracy theories and their tendency to engage in conspiratorial thinking. The four studies, including materials, hypotheses, and analyses, were pre-registered and all materials and data are accessible via the Open Science Framework (\url{https://osf.io/8utsj/?view_only=364478f01fc548d0a42b9962918d871d}). The differences between the four studies are summarized presently, and the methods are detailed below.
